\SuperScreen: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2022-07-18 main.tex
remove \textcolor and fix two typos

@@

\SuperScreen is a Python package developed to simulate the static magnetic response of structures composed of one or more layers containing superconducting thin films characterized by a London penetration depth $\lambda$ that is large compared to the film thickness $d$. \SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films in the presence of inhomogeneous applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt2004-ew,Brandt2005-wj} and subsequently used by Kirtley, \emph{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors~\cite{Kirtley2016-zz, Kirtley2016-gt}.

There have been many previous numerical studies of magnetic screening and inductance extraction in thin film and two-dimensional (2D) superconducting devices~\cite{Jaycox1981-zl, Ketchen1982-at, Ketchen2012-mb, Hildebrandt1995-uw, Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev,  Babaei_Brojeny2003-la, Brandt2004-ew, Brandt2005-wj, Clem2005-ye, Muller2021-ci, Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}. However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}, and a more thorough overview in Ref.~\cite{Gaj1999-ls}.} Most of these tools are intended for use in the design of superconducting integrated circuits for single flux quantum (SFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls, Tolpygo2021-jz}. \SuperScreen is an open-source, user-friendly, portable research tool designed to lower the barrier to entry to quantitative modeling of 2D superconductors, and to help interpret and inform measurements of superconducting thin films and devices.

This introduction to \SuperScreen is organized as follows: In Section~\ref{section:model} we outline the model and its assumptions, and in Section~\ref{section:implementation} we describe its numerical implementation. In Section~\ref{section:overview} we provide an overview of the structure of the \SuperScreen package and discuss some important development details. In Section~\ref{section:examples} we demonstrate how to perform several types of simulations using \SuperScreen and compare the results to analytical solutions and experimental results. Finally, in Section~\ref{section:conlusion} we conclude by discussing applications, limitations, and possible extensions of the package. Python scripts and Jupyter notebooks used to generate all figures presented below can be found in the GitHub repository accompanying this manuscript~\cite{logan_bishop_van_horn_2022_6363541}.

@@

A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}. In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda$ obey the second London equation:
$\vec{H}(\vec{r})-\lambda^2\vec{\nabla}\times\vec{j}(\vec{r})=$, where
$\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$ is the 3D gradient operator. The 2D London model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$. Working now with the thickness-integrated current density $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
is the thickness of the film, the second London equation reduces to
\begin{equation}
    \label{eq:london}
    \vec{H}(x, y)=-\Lambda\vec{\nabla}\times\vec{J}(x, y)\\
\end{equation}
where $\Lambda=\lambda^2/d$ is the effective penetration depth
of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}) and $\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}\right)$ is now the 2D gradient operator.

It is important to note that the assumption $\vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ is valid for only films that are thinner than their London penetration depth ($d\ll\lambda$, such that $\Lambda=\lambda^2/d\gg\lambda$). However the model has been applied with some success in structures with $\lambda\lesssim d$, for example by Kirtley, \emph{et al.} in modeling the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz,Kirtley2016-gt}. Aside from this limitation, the method described below can be used to model films with any effective penetration depth $0\leq\Lambda<\infty$.

@@

layer = sc.Layer(
    "base",
    london_lambda=0.24,
    thickness=0.2,
)
film = sc.Polygon(
    "washer",
    layer="base",
    points=box(30, points_per_side=50),
)
hole = sc.Polygon(
    "hole",
    layer="base",
    points=box(10, points_per_side=250),
)
device = sc.Device(
    "washer",
    layers=[layer],
    films=[film],
    holes=[hole],
    length_units="um",
)
device.make_mesh(min_points=3000)
# See Equation 19.
M = device.mutual_inductance_matrix()
L = M[0, 0].to("pH")
print(f"Inductance = {L:~.4fP}")
# Output: Inductance = 19.9100 pH
\end{minted}
\captionof{listing}{\SuperScreen script to calculate the self-inductance of a square washer with outer dimension $30\,\um$, inner dimension $10\,\um$, London penetration depth $\lambda=0.24\,\um$, and film thickness $d=0.20\,\um$. The extracted inductance $L=19.91\,\mathrm{pH}$ differs from the InductEx ``design'' and ``extracted'' values by -0.45\% and -0.92\% respectively~\cite{inductex_user_manual_2020}. }
\label{code:washer}
\end{code-onecol}

@@

The London equation (Equation~\ref{eq:london}) is valid only under the assumption that the London penetration depth $\lambda$, a proxy for the superfluid density, is constant as a function of position~\cite{Tinkham2004-zn}. In cases where the superfluid density varies as a function of position, Ginzburg-Landau theory provides a more accurate description of the magnetic response of the system. Nevertheless, in an effort to model inhomogeneous superconductors using London theory, one can write out the ``inhomogeneous second London equation'' for a superconductor with spatially-varying London penetration depth $\lambda(\vec{r})$~\cite{Cave1986-js, Kogan2011-zn}:
\begin{align}
\begin{split}
    \label{eq:london_inhomogeneous_3d}
    \vec{H}(\vec{r})&=-\vec{\nabla}\times\left(\lambda^2(\vec{r})\vec{j}(\vec{r})\right)\\
    &=-\left(\lambda^2(\vec{r})\vec{\nabla}\times\vec{j}(\vec{r}) + \vec{\nabla}\lambda^2(\vec{r})\times\vec{j}(\vec{r})\right).
\end{split}
\end{align}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{examples/images/xlarge-dz-dr.pdf}
    \caption{\SuperScreen results may be unreliable for multi-layer models where the spacing between layers is smaller than the typical vertex-to-vertex distance, $\delta r$. ({\bf a}) Field coil - pickup loop mutual inductance for the largest SQUID suscepometer modeled in Section~\ref{section:examples:scanning-squid} as a function of the minimum vertical spacing between layers, $\delta z$. The simulated mutual inductance is shown with blue circles, and a histogram of the mesh vertex-to-vertex distances $\delta r$ is shown in orange (arb. $y$ axis units). When $\delta z\lesssim\delta r$, the model significantly overestimates the mutual inductance. ({\bf b}) and ({\bf c}): Out-of-plane magnetic field $\mu_0H_z$ evaluated at the plane of the pickup loop (W1 layer) for ({\bf b}) the nominal layer spacing with $\delta z<\delta 2$ (indicated with a black $\times$ in ({\bf a})) and ({\bf c}) $\delta z > \delta r$ (indicated with a black $+$ in ({\bf a})). For $\delta r\lesssim\delta z$, the magnet field calculated using Eq.~\ref{eq:hz-from-kernel} resembles that of a discrete set of isolated dipoles rather than a continuous sheet of current. Note that ({\bf b}) and ({\bf c}) share the same color scale, which is saturated in ({\bf b}).}
    \label{fig:xlarge-dz-dr}
\end{figure}

>>>>

% \usepackage{ulem,xcolor}

@@

\SuperScreen is a Python package developed to simulate the static magnetic response of structures composed of one or more layers containing superconducting thin films characterized by a London penetration depth $\lambda$ that is large compared to the film thickness $d$. \SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films in the presence of inhomogeneous applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt2004-ew,Brandt2005-wj} and subsequently used by Kirtley, \textit{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors~\cite{Kirtley2016-zz, Kirtley2016-gt}.

There have been many previous numerical studies of magnetic screening and inductance extraction in thin film and two-dimensional (2D) superconducting devices~\cite{Jaycox1981-zl, Ketchen1982-at, Ketchen2012-mb, Hildebrandt1995-uw, Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev,  Babaei_Brojeny2003-la, Brandt2004-ew, Brandt2005-wj, Clem2005-ye, Muller2021-ci, Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}. However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}.} Most of these tools are intended for use in the design of superconducting integrated circuits for single flux quantum (SFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls, Tolpygo2021-jz}. \SuperScreen is an open-source, user-friendly, portable research tool designed to lower the barrier to entry to quantitative modeling of 2D superconductors, and to help interpret and inform measurements of superconducting thin films and devices.

This introduction to \SuperScreen is organized as follows: In Section~\ref{section:model} we outline the model and its assumptions, and in Section~\ref{section:implementation} we describe its numerical implementation. In Section~\ref{section:overview} we provide an overview of the structure of the \SuperScreen package and discuss some important development details. In Section~\ref{section:examples} we demonstrate how to perform several types of simulations using \SuperScreen and compare the results to analytical solutions and experimental results. Finally, in Section~\ref{section:conlusion} we conclude by discussing applications, limitations, and possible extensions of the package.

@@

A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}. In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda$ obey the second London equation:
$\vec{H}(\vec{r})/\lambda^2=-\vec{\nabla}\times\vec{j}(\vec{r})$, where
$\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$ is the 3D gradient operator. The 2D London model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$. Working now with the thickness-integrated current density $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
is the thickness of the film, the second London equation reduces to

\begin{equation}
    \label{eq:london}
    \vec{H}(x, y)=-\Lambda\vec{\nabla}\times\vec{J}(x, y)
\end{equation}
where $\Lambda=\lambda^2/d$ is the effective penetration depth
of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}) and $\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}\right)$ is now the 2D gradient operator.

It is important to note that the assumption $\vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ is valid for only films that are thinner than their London penetration depth ($d\ll\lambda$, such that $\Lambda=\lambda^2/d\gg\lambda$). However the model has been applied with some success in structures with $\lambda\lesssim d$, for example by Kirtley, \textit{et al.} in modeling the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz,Kirtley2016-gt}. Aside from this limitation, the method described below can be used to model films with any effective penetration depth $0\leq\Lambda<\infty$.

@@

layer = sc.Layer(
    "base",
    london_lambda=0.24,
    thickness=0.2,
)
film = sc.Polygon(
    "washer",
    layer="base",
    points=box(30, points_per_side=50),
)
hole = sc.Polygon(
    "hole",
    layer="base",
    points=box(10, points_per_side=250),
)
device = sc.Device(
    "washer",
    layers=[layer],
    films=[film],
    holes=[hole],
    length_units="um",
)
device.make_mesh(min_points=3000)
# See Equation 19.
M = device.mutual_inductance_matrix()
L = M[0, 0].to("pH")
print(f"Inductance = {L:~.4fP}")
# Output: Inductance = 19.9100 pH
\end{minted}
\captionof{listing}{\SuperScreen script to calculate the self-inductance of a square washer with outer dimension $30\,\um$, inner dimension $10\,\um$, London penetration depth $\lambda=0.24\,\um$, and film thickness $d=0.20\,\um$. The extracted inductance $L=19.91\,\mathrm{pH}$ differs from the InductEx ``design'' and ``extracted'' values by -0.45\% and -0.92\% respectively~\cite{inductex_user_manual_2020}.}
\label{code:washer}
\end{code-onecol}

@@

The London equation (Equation~\ref{eq:london}) is valid only under the assumption that the London penetration depth $\lambda$, a proxy for the superfluid density, is constant as a function of position~\cite{Tinkham2004-zn}. In cases where the superfluid density varies as a function of position, Ginzburg-Landau theory provides a more accurate description of the magnetic response of the system. Nevertheless, in an effort to model inhomogeneous superconductors using London theory, one can write out the ``inhomogeneous second London equation'' for a superconductor with spatially-varying London penetration depth $\lambda(\vec{r})$~\cite{Cave1986-js, Kogan2011-zn}:

\begin{align}
\begin{split}
    \label{eq:london_inhomogeneous_3d}
    \vec{H}(\vec{r})&=-\vec{\nabla}\times\left(\lambda^2(\vec{r})\vec{j}(\vec{r})\right)\\
    &=-\left(\lambda^2(\vec{r})\vec{\nabla}\times\vec{j}(\vec{r}) + \vec{\nabla}\lambda^2(\vec{r})\times\vec{j}(\vec{r})\right).
\end{split}
\end{align}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{examples/images/xlarge-dz-dr.pdf}
    \caption{\SuperScreen results may be unreliable for multi-layer models where the spacing between layers is smaller than the typical vertex-to-vertex distance, $\delta r$. ({\bf a}) Field coil - pickup loop mutual inductance for the largest SQUID suscepometer modeled in Section~\ref{section:examples:scanning-squid} as a function of the minimum vertical spacing between layers, $\delta z$. The simulated mutual inductance is shown with blue circles, and a histogram of the mesh vertex-to-vertex distances $\delta r$ is shown in orange (arb. $y$ axis units). When $\delta z\lesssim\delta r$, the model significantly overestimates the mutual inductance. ({\bf b}) and ({\bf c}): Out-of-plane magnetic field $\mu_0H_z$ evaluated at the plane of the pickup loop (W1 layer) for ({\bf b}) the nominal layer spacing with $\delta z<\delta r$ (indicated with a black $\times$ in ({\bf a})) and ({\bf c}) $\delta z > \delta r$ (indicated with a black $+$ in ({\bf a})). For $\delta r\lesssim\delta z$, the magnetic field calculated using Eq.~\ref{eq:hz-from-kernel} resembles that of a discrete set of isolated dipoles rather than a continuous sheet of current. Note that ({\bf b}) and ({\bf c}) share the same color scale, which is saturated in ({\bf b}).}
    \label{fig:xlarge-dz-dr}
\end{figure}
